\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-10 paper/paper.tex
Revert "Small edit"
This reverts commit a3c23a10574b2b4c124b0bb16e9f3f4ade2d96e3.

The set of model specifications were chosen based on the data, interpretation of the model, as well as estimation considerations. Drive brand specific parameters for the the wearout failure mode $(\mu_{d2},\sigma_{d2})$, and the proportion defective $(\pi_d)$, are considered as a means to account for heterogeneity across brands in the right tails of the failure distribution.  Going from a common model for all hard drive brands and gradually increasing the complexity of the model, we end up at Model 4.  Model 4 allows for the probability of infant mortality as well as the shape and scale parameters for the 2nd failure mode to vary by brand drive model.

@@

\subsection{Priors}
To complete the full probability model, we need to select prior distributions for the parameters governing the hierarchical model. We select proper priors to ensure a proper posterior. For the scale hyper-parameters we follow the recommendations of \citet{gelman2014bayesian} and use half-Cauchy priors. As for the location hyper-parameters, we select weakly informative priors consistent with our prior information on hard-drives. The prior for $\eta_\pi$ puts 95\% of prior mass on the interval $(0.006, 0.27)$ for the median proportion defective (What justification? Should maybe be lower.) For $\eta_{\sigma, 2}$, 95\% of prior mass is on values greater than $0.037$. Since $\sigma_d$ is the reciprocal of the Weibull shape parameter, this correponds roughly to an assumption that the median Weibull shape parameter is less than $1/0.037 = 27$. The prior for $\eta_{t_{p_2},2}$ implies that the median 20th percentile for non-defective units is less than greater than 3 days and less than 24 years.

>>>>

The set of model specifications were chosen based on the data, interpretation of the model, as well as estimation considerations. Drive brand specific parameters for the the wearout failure mode $(\mu_{d2},\sigma_{d2})$, and the proportion defective $(\pi_d)$, are considered to account for heterogeneity across brands in the right tails of the failure distribution.  Going from a common model for all hard drive brands and gradually increasing the complexity of the model, we end up at Model 4.  Model 4 allows for the probability of infant mortality as well as the shape and scale parameters for the 2nd failure mode to vary by brand drive model.

@@

\subsection{Priors}
To complete the full probability model, we need to select prior distributions for the parameters governing the hierarchical model. We select proper priors to ensure a proper posterior. For the scale hyper-parameters we follow the recommendations of \citet{gelman2014bayesian} and use half-Cauchy priors. As for the location hyper-parameters, we select weakly informative priors consistent with our prior information on hard-drives. The prior for $\eta_\pi$ puts 95\% of prior mass on the interval $(0.006, 0.27)$ for the median proportion defective (What justification? Should maybe be lower.) For $\eta__{\sigma, 2}$, 95\% of prior mass is on values greater than $0.037$. Since $\sigma_d$ is the reciprocal of the Weibull shape parameter, this correponds roughly to an assumption that the median Weibull shape parameter is less than $1/0.037 = 27$. The prior for $\eta_{t_{p_2},2}$ implies that the median 20th percentile for non-defective units is less than greater than 3 days and less than 24 years.
